------------------------------------------------------Buga Anna------------------

```{r}

```

#Import csv file:

```{r}
info=read.csv("EcommerceSalesData.csv")
placement=data.frame(info)
info
```

```{r}
library("ggplot2")
info1<-ggplot(placement,aes(x=Day_of_Week, y=price, fill=category))+geom_dotplot(stat="identity", colour="black", position="dodge")+theme(plot.title = element_text(hjust = 0.5, face="bold"))+labs(title = "Day_Week_sales")
info1+ xlab("Day of Week") + ylab("Price")
```

more sales in Sunday

#part 2

```{r}

nmbrPopulation<- 50000*(25/100)
```

```{r}
#12%
Population_Buyers <- nmbrPopulation * (12/100)
SalesAfterTV_ADV <- 1500
```

```{r}
```

```{r}
SalesBeforeTV_ADV <- sum(info1$price)
```

```{r}
InvestmentTV <- 15000
Profit <- SalesAfterTV_ADV - InvestmentTV
GrowTV <- 100*round(SalesAfterTV_ADV / SalesBeforeTV_ADV, 2)
`

```

```{r}
print(paste("SalesBeforeTV_ADV =","$",SalesBeforeTV_ADV))
print(paste("SalesAfterTV_ADV =","$",SalesAfterTV_ADV))
print(paste("Growth Rate =",GrowTV, "%"))
print(paste("Profit =","$",Profit))
print("After investment 15,000  the new sales = 1,500")
print("loss $13.500")
```

#part3

```{r}
nmbrPopulation <- 50000 * (10/100)
Population_Buyers <- Population * (5/100)
SalesAfterRadio_ADV <- 500
SalesBeforeRadio_ADV <- sum(info1$price)
InvestmentRD <- 15000
Profit <- SalesAfterRadio_ADV - InvestmentRD
Sales <- 100 * round(SalesAfterRadio_ADV / SalesBeforeRadio_ADV, 2)
```

```{r}
print(paste("SalesBeforeRadio_ADV =","$",SalesBeforeRadio_ADV))
print(paste("SalesAfterRadio_ADV =","$",SalesAfterRadio_ADV))
print(paste("Growth Rate =",Sales, "%"))
print(paste("Profit =","$",Profit))
print("lost $14.500")
```

part4

```{r}
SalesGrowthTV <- SalesAfterTV_ADV - SalesBeforeTV_ADV
ROI_TV <- round(SalesGrowthTV / InvestmentTV *100, 2)
print(paste("ROI for TV =",ROI_TV, "%"))

```

```{r}
SalesGrowthRD <- SalesAfterRadio_ADV - SalesBeforeRadio_ADV
ROI_RD <- round(SalesGrowthRD / InvestmentRD *100, 2)
print(paste("ROI for Radio =",ROI_RD, "%"))
```

```{r}
info1<-ggplot(placement,aes(x=SalesAfterRadio_ADV,y=SalesBeforeTV_ADV, fill=category))+geom_area()+labs(title = "sales")
info1+ xlab("SalesAfterRadio_ADV") + ylab("SalesBeforeTV_ADV")
```

```{r}

```

```{r}
```

dd a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
